---
title: "Class stuff"
author: "Matthew Curran"
date: "October 15, 2019"
output: github_document
---

```{r setup, include=FALSE}
library(rvest)
library(p8105.datasets)
library(tidyverse)
```

##Playing with strings
```{r}
string_vec = c("my", "name", "is", "jeff")

str_detect(string_vec, "jeff")

str_detect(string_vec, "m")
```

```{r}
str_replace(string_vec, "jeff", "Jeff")
```

```{r}
string_vec = c(
  "i think we all rule for participating",
  "i think i have been caught",
  "i think this will be quite fun actually",
  "it will be fun, i think"
  )

str_detect(string_vec, "^i think")

str_detect(string_vec, "i think$")
```

##Shows "bush" that starts with capital or lowercase but is lowercase after.
```{r}
string_vec = c(
  "Y'all remember Pres. HW Bush?",
  "I saw a green bush",
  "BBQ and Bushwalking at Molonglo Gorge",
  "BUSH -- LIVE IN CONCERT!!"
  )

str_detect(string_vec,"[Bb]ush")
```

```{r}
string_vec = c(
  '7th inning stretch',
  '1st half soon to begin. Texas won the toss.',
  'she is 5 feet 4 inches tall',
  '3AM - cant sleep :('
  )

str_detect(string_vec, "^[0-9][a-zA-Z]")
```

```{r}
string_vec = c(
  'Its 7:11 in the evening',
  'want to go to 7-11?',
  'my flight is AA711',
  'NetBios: scanning ip 203.167.114.66'
  )

str_detect(string_vec, "7.11")
```
 ##Some characters are “special”. These include [ and ], ( and ), and .. If you want to search for these, you have to indicate they’re special using \. Unfortunately, \ is also special, so things get weird.
```{r}
string_vec = c(
  'The CI is [2, 5]',
  ':-]',
  ':-[',
  'I found the answer on pages [6-7]',
  '[..4]'
  )

str_detect(string_vec, "\\[")
str_detect(string_vec, "\\[.")
str_detect(string_vec, "\\[\\.")
```

* So do not usethe second of the detects in above chunk, needs a double slash for every special character


```{r}
pulse_data = 
  haven::read_sas("./data/public_pulse_data.sas7bdat") %>%
  janitor::clean_names() %>%
  pivot_longer(
    bdi_score_bl:bdi_score_12m,
    names_to = "visit", 
    names_prefix = "bdi_score_",
    values_to = "bdi") %>%
  select(id, visit, everything()) %>%
  mutate(
    visit = str_replace(visit, "bl", "00m"),
    visit = fct_relevel(visit, str_c(c("00", "01", "06", "12"), "m"))) %>%
  arrange(id, visit)

print(pulse_data, n = 12)
```

```{r}
devtools::install_github("benmarwick/wordcountaddin", type = "source", dependencies = TRUE)

```


# Lecture November 7 Linear Model
```{r word cout}
library(tidyverse)
library(viridis)
library(p8105.datasets)
library(plotly)

set.seed(1)
```

```{r}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>% 
  rename(
    boro = neighbourhood_group,
    neighborhood = neighbourhood) %>% 
  filter(boro != "Staten Island") %>% 
  select(price, stars, boro, neighborhood, room_type)
```

Fit a first linear model.

```{r}
fit = lm(price ~ stars + boro, data = nyc_airbnb)

fit

summary(fit)

coef(fit)
```

```{r}
fit%>%
  broom::tidy()%>%
  mutate(term=str_replace(term, "boro", "Boro: "))%>%
  knitr::kable(digits = 3)
```

factors

```{r}
nyc_airbnb=
  nyc_airbnb%>%
  mutate(
    boro = fct_infreq(boro),
    room_type = fct_infreq(room_type)
  )
```


Cross Validation

```{r}
library(tidyverse)
library(modelr)
library(mgcv)
set.seed(1)
```

```{r}
nonlin_df = 
  tibble(
    id = 1:100,
    x = runif(100, 0, 1),
    y = 1 - 10 * (x - .3) ^ 2 + rnorm(100, 0, .3)
  )

nonlin_df %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point() + theme_bw()
```

```{r}
train_df = sample_n(nonlin_df, 80)
test_df = anti_join(nonlin_df, train_df, by = "id")

ggplot(train_df, aes(x = x, y = y)) + 
  geom_point() + 
  geom_point(data = test_df, color = "red")
```
# Fit 3 models of varying goodness
```{r}
linear_mod = lm(y ~ x, data = train_df)
smooth_mod = mgcv::gam(y ~ s(x), data = train_df)
wiggly_mod = mgcv::gam(y ~ s(x, k = 30), sp = 10e-6, data = train_df)


train_df %>% 
  add_predictions(linear_mod) %>% 
  ggplot(aes(x = x, y = y)) + geom_point() + 
  geom_line(aes(y = pred), color = "red")

train_df %>% 
  add_predictions(smooth_mod) %>% 
  ggplot(aes(x = x, y = y)) + geom_point() + 
  geom_line(aes(y = pred), color = "red")

train_df %>% 
  add_predictions(wiggly_mod) %>% 
  ggplot(aes(x = x, y = y)) + geom_point() + 
  geom_line(aes(y = pred), color = "red")
```

## Use this to see all 3 models at once.
```{r}
train_df %>% 
  gather_predictions(linear_mod, smooth_mod, wiggly_mod) %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point() + 
  geom_line(aes(y = pred), color = "red") + 
  facet_wrap(~model)
```

##Test them - smaller numbers are better
```{r}
rmse(linear_mod, test_df)

rmse(smooth_mod, test_df)

rmse(wiggly_mod, test_df)
```

# Do all this CV using modelr

```{r}
cv_df = 
  crossv_mc(nonlin_df, 100) 

cv_df %>% pull(train) %>% .[[1]] %>% as_tibble

cv_df %>% pull(test) %>% .[[1]] %>% as_tibble

cv_df =
  cv_df %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))
```

```{r}
cv_df = 
  cv_df %>% 
  mutate(linear_mod  = map(train, ~lm(y ~ x, data = .x)),
         smooth_mod  = map(train, ~mgcv::gam(y ~ s(x), data = .x)),
         wiggly_mod  = map(train, ~gam(y ~ s(x, k = 30), sp = 10e-6, data = .x))) %>% 
  mutate(rmse_linear = map2_dbl(linear_mod, test, ~rmse(model = .x, data = .y)),
         rmse_smooth = map2_dbl(smooth_mod, test, ~rmse(model = .x, data = .y)),
         rmse_wiggly = map2_dbl(wiggly_mod, test, ~rmse(model = .x, data = .y)))

cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```


# Bootstrapping
```{r}
library(tidyverse)
library(p8105.datasets)

set.seed(1)

n_samp = 250

sim_df_const = 
  tibble(
    x = rnorm(n_samp, 1, 1),
    error = rnorm(n_samp, 0, 1),
    y = 2 + 3 * x + error
  )

sim_df_nonconst = sim_df_const %>% 
  mutate(
  error = error * .75 * x,
  y = 2 + 3 * x + error
)

sim_df = 
  bind_rows(const = sim_df_const, nonconst = sim_df_nonconst, .id = "data_source") 

sim_df %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point(alpha = .5) +
  stat_smooth(method = "lm") +
  facet_grid(~data_source) 

lm(y ~ x, data = sim_df_const) %>% 
  broom::tidy() %>% 
  knitr::kable(digits = 3)

lm(y ~ x, data = sim_df_nonconst) %>% 
  broom::tidy() %>% 
  knitr::kable(digits = 3)
```

```{r}
boot_sample = function(df) {
  sample_frac(df, replace = TRUE)
} %>%
  arrange(x)

boot_sample(sim_df_nonconst) %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point(alpha = .5) +
  stat_smooth(method = "lm")

boot_straps = 
  data_frame(
    strap_number = 1:1000,
    strap_sample = rerun(1000, boot_sample(sim_df_nonconst))
  )

boot_straps

boot_straps %>% 
  filter(strap_number %in% 1:2) %>% 
  mutate(strap_sample = map(strap_sample, ~arrange(.x, x))) %>% 
  pull(strap_sample)

boot_straps %>% 
  filter(strap_number %in% 1:3) %>% 
  unnest(strap_sample) %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point(alpha = .5) +
  stat_smooth(method = "lm", se = FALSE) +
  facet_grid(~strap_number) 
```

```{r}
bootstrap_results = 
  boot_straps %>% 
  mutate(
    models = map(strap_sample, ~lm(y ~ x, data = .x) ),
    results = map(models, broom::tidy)) %>% 
  select(-strap_sample, -models) %>% 
  unnest() %>% 
  group_by(term) %>% 
  summarize(boot_se = sd(estimate))
## Warning: `cols` is now required.
## Please use `cols = c(results)`

bootstrap_results %>% 
  knitr::kable(digits = 3)

boot_straps %>% 
  unnest(strap_sample) %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_line(aes(group = strap_number), stat = "smooth", method = "lm", se = FALSE, alpha = .1, color = "blue") +
  geom_point(data = sim_df_nonconst, alpha = .5)

boot_straps = 
  sim_df_nonconst %>% 
  modelr::bootstrap(n = 1000)

boot_straps$strap[[1]]

as_data_frame(boot_straps$strap[[1]])

sim_df_nonconst %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(y ~ x, data = .x) ),
    results = map(models, broom::tidy)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  group_by(term) %>% 
  summarize(boot_se = sd(estimate))

sim_df_const %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(models = map(strap, ~lm(y ~ x, data = .x) ),
         results = map(models, broom::tidy)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  group_by(term) %>% 
  summarize(boot_se = sd(estimate))
```

## Bootstrapping with Airbnb

```{r}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>% 
  rename(
    boro = neighbourhood_group,
    neighborhood = neighbourhood) %>% 
  filter(boro != "Staten Island") %>% 
  select(price, stars, boro, neighborhood, room_type)

nyc_airbnb %>% 
  ggplot(aes(x = stars, y = price, color = room_type)) + 
  geom_point() 

nyc_airbnb %>% 
  filter(boro == "Manhattan") %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~ lm(price ~ stars + room_type, data = .x)),
    results = map(models, broom::tidy)) %>% 
  select(results) %>% 
  unnest(results) %>% 
  filter(term == "stars") %>% 
  ggplot(aes(x = estimate)) + geom_density()
```


