---
title: "Class stuff"
author: "Matthew Curran"
date: "October 15, 2019"
output: github_document
---

```{r setup, include=FALSE}
library(rvest)
library(p8105.datasets)
library(tidyverse)
```

##Playing with strings
```{r}
string_vec = c("my", "name", "is", "jeff")

str_detect(string_vec, "jeff")

str_detect(string_vec, "m")
```

```{r}
str_replace(string_vec, "jeff", "Jeff")
```

```{r}
string_vec = c(
  "i think we all rule for participating",
  "i think i have been caught",
  "i think this will be quite fun actually",
  "it will be fun, i think"
  )

str_detect(string_vec, "^i think")

str_detect(string_vec, "i think$")
```

##Shows "bush" that starts with capital or lowercase but is lowercase after.
```{r}
string_vec = c(
  "Y'all remember Pres. HW Bush?",
  "I saw a green bush",
  "BBQ and Bushwalking at Molonglo Gorge",
  "BUSH -- LIVE IN CONCERT!!"
  )

str_detect(string_vec,"[Bb]ush")
```

```{r}
string_vec = c(
  '7th inning stretch',
  '1st half soon to begin. Texas won the toss.',
  'she is 5 feet 4 inches tall',
  '3AM - cant sleep :('
  )

str_detect(string_vec, "^[0-9][a-zA-Z]")
```

```{r}
string_vec = c(
  'Its 7:11 in the evening',
  'want to go to 7-11?',
  'my flight is AA711',
  'NetBios: scanning ip 203.167.114.66'
  )

str_detect(string_vec, "7.11")
```
 ##Some characters are “special”. These include [ and ], ( and ), and .. If you want to search for these, you have to indicate they’re special using \. Unfortunately, \ is also special, so things get weird.
```{r}
string_vec = c(
  'The CI is [2, 5]',
  ':-]',
  ':-[',
  'I found the answer on pages [6-7]',
  '[..4]'
  )

str_detect(string_vec, "\\[")
str_detect(string_vec, "\\[.")
str_detect(string_vec, "\\[\\.")
```

* So do not usethe second of the detects in above chunk, needs a double slash for every special character


```{r}
pulse_data = 
  haven::read_sas("./data/public_pulse_data.sas7bdat") %>%
  janitor::clean_names() %>%
  pivot_longer(
    bdi_score_bl:bdi_score_12m,
    names_to = "visit", 
    names_prefix = "bdi_score_",
    values_to = "bdi") %>%
  select(id, visit, everything()) %>%
  mutate(
    visit = str_replace(visit, "bl", "00m"),
    visit = fct_relevel(visit, str_c(c("00", "01", "06", "12"), "m"))) %>%
  arrange(id, visit)

print(pulse_data, n = 12)
```

```{r}
devtools::install_github("benmarwick/wordcountaddin", type = "source", dependencies = TRUE)

```


# Lecture November 7 Linear Model
```{r word cout}
library(tidyverse)
library(viridis)
library(p8105.datasets)
library(plotly)

set.seed(1)
```

```{r}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>% 
  rename(
    boro = neighbourhood_group,
    neighborhood = neighbourhood) %>% 
  filter(boro != "Staten Island") %>% 
  select(price, stars, boro, neighborhood, room_type)
```

Fit a first linear model.

```{r}
fit = lm(price ~ stars + boro, data = nyc_airbnb)

fit

summary(fit)

coef(fit)
```

```{r}
fit%>%
  broom::tidy()%>%
  mutate(term=str_replace(term, "boro", "Boro: "))%>%
  knitr::kable(digits = 3)
```

factors

```{r}
nyc_airbnb=
  nyc_airbnb%>%
  mutate(
    boro = fct_infreq(boro),
    room_type = fct_infreq(room_type)
  )
```



